Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development

### 2017-01-06 jssst/paper.tex
Add Chosha Shoukai

% \begin{choshashoukai}
%
% \chosha{山本拓朗}
% {2016年大阪大学基礎工学部システム科学科卒．
% }
% \chosha{大山博司}
% {
% }
% \chosha{安積卓也}
% {
% }
%
% \end{choshashoukai}

>>>>

\begin{choshashoukai}

\chosha{Takuro Yamamoto}
{
Takuro Yamamoto received his B.E. degree from Osaka University in 2016. His research interests include real-time and embedded systems.
}
\chosha{Hiroshi Oyama}
{
Hiroshi Oyama received Dr. Engineering degree from Gifu University in 2002.
He works at Okuma Corporation as Senior Engineer and also works at Nagoya University as Visiting Professor.
He is studying software components and programming language for embedded systems.
}
\chosha{Takuya Azumi}
{
Takuya Azumi is an Assistant Professor at the Graduate School of Engineering Science, Osaka University. 
He received his Ph.D. degree from the Graduate School of Information Science, Nagoya University.
From 2008 to 2010, he was under the research fellowship for young scientists for Japan Society for the Promotion of Science.
From 2010 to 2014, he was an Assistant Professor at the College of Information Science and Engineering, Ritsumeikan University.
His research interests include real-time operating systems and component based development.
He is a member of IEEE, ACM, IPSJ, and IEICE.
}

\end{choshashoukai}
